Investigation of the Effect of Pretraining on EEG Classification with Deep Recurrent-Convolutional Networks

### 2017-10-15 paper/paper.tex
Results/evaluation section

We used 8-fold validation for our results.

@@

>>>>

\subsubsection{Evaluation}
Because of a very small amount of data available (766 samples in total), we have decided to use n-fold cross-validation (with \textit{n=8}) as the evaluation method. The data has been shuffled before being split into folds. For each of the $n$ runs, weights for the model with the lowest validation loss have been saved. The model's performance has then been measured on the validation fold. Final accuracy has then been computed as an average over all the runs.
Cross-validation has also been used to evaluate the baseline methods (per each method, per each configuration of parameters).
\newline
The Neural Network models have been trained on mini batches of size 32, using Adam \cite{Adam} as the optimization method.

@@

	\bibitem{Adam}
	Kingma, D. P. \& Ba, J. (2014). 
	\textit{Adam: A Method for Stochastic Optimization.} 
	CoRR, abs/1412.6980.
